\textbf{Using the MSU Thesis Class}

### 2024-02-19 docs/msu-thesis.tex
4.1g (internal changes only)
v4.2 fixed spacing issue with successive section headings

\def\msuversion{4.1g}
\def\msudate{2023/08/12}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of 
the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks 
to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the 
landscape page numbering code, which greatly simplified my original version. Thanks to 
Florent Chervet for early \pkg{hyperref} code (up until v.3.6), and Ulrike Fischer for the 
current \pkg{hyperref} code.  Thanks also to the following students who have reported 
problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, 
Nathan Brugnone, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk 
Jung, Claire Kopenhafer, Adam Liter, Vanessa Maldonado, Andriana Manousidaki, Ben Miller, William Muir, Eureka 
Pai, Alicia Parrish, Neil ver Planck, Taha Posos, Nick Rekuski, Giacomo Romanini, William Sands, Adam 
Soliman, Mookyong Son, Erik Stitt, Fanurs C.E. Teh,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali 
Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy 
of his entire thesis which allowed me to debug some especially subtle spacing 
inconsistencies.

>>>>

\def\msuversion{4.2}
\def\msudate{2024/02/18}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

Version 4.2 changed the spacing parameters for subsections to appease the thesis office yet again.

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of 
the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks 
to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the 
landscape page numbering code, which greatly simplified my original version. Thanks to 
Florent Chervet for early \pkg{hyperref} code (up until v.3.6), and Ulrike Fischer for the 
current \pkg{hyperref} code.  Thanks to David Carlisle for helping me understand a ridiculous spacing problem. 
Thanks also to the following students who have reported 
problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, 
Nathan Brugnone, Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk 
Jung, Claire Kopenhafer, Adam Liter, Vanessa Maldonado, Andriana Manousidaki, Ben Miller, William Muir, Eureka 
Pai, Alicia Parrish, Neil ver Planck, Taha Posos, Nick Rekuski, Giacomo Romanini, William Sands, Adam 
Soliman, Mookyong Son, Erik Stitt, Fanurs C.E. Teh,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Atacan Yücesoy, Ali 
Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy 
of his entire thesis which allowed me to debug some especially subtle spacing 
inconsistencies.
